### 2012-07-04 inst/examples/bias_table.Rmd
bias table, more reps

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

``` {r }
xmin <- 0
xmax <- 2.5 * K
grid_n <- 200
````

@@

``` {r }
pars <- c(r, K)
````

``` {r  }
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

``` {r  }
opt_low <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r }
pars <- c(r, K)
````

``` {r  }
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

``` {r  }
opt_med <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r }
pars <- c(r, K)
````

``` {r  }
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

``` {r  }
opt_high <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(low=opt_low, med=opt_med, high=opt_high)
par_list <- list(c(1, 100), c(1.5, 100), c(2, 100))

@@

# References

``` {r biblio, echo=FALSE, results="asis"}
knitcitations::bibliography("html")
````

>>>>

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
````

@@

``` {r }
xmin <- 0
xmax <- 2.5 * K
grid_n <- 300
````

@@

``` {r }
pars1 <- c(r, K)
````

``` {r  }
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat1 <- determine_SDP_matrix(f, pars1, x_grid, h_grid, sigma_g, pdfn)
````

``` {r  }
opt_low <- find_dp_optim(SDP_Mat1, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r }
pars2 <- c(r, K)
````

``` {r  }
SDP_Mat2 <- determine_SDP_matrix(f, pars2, x_grid, h_grid, sigma_g, pdfn)
````

``` {r  }
opt_med <- find_dp_optim(SDP_Mat2, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r }
pars3 <- c(r, K)
````

``` {r  }
SDP_Mat3 <- determine_SDP_matrix(f, pars3, x_grid, h_grid, sigma_g, pdfn)
````

``` {r  }
opt_high <- find_dp_optim(SDP_Mat3, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(low=opt_low, med=opt_med, high=opt_high)
par_list <- list(pars1, pars2, pars3)

@@

``` {r printvalue}
k <- which.min(abs(K-x_grid))
data.frame(low=opt_low$V[k], med=opt_med$V[k], high=opt_high$V[k])
```
